Death Registrations May Indicate a Discreptency in Reported Data During the COVID-19 Pandemic

### 2023-02-03 outputs/paper/paper.qmd
updated readme and license

---
title: "Death Registrations May Indicate a Discreptency Between Expected and Reported Data During the COVID-19 Pandemic"
subtitle: "An Analysis of Death Registrations from 2016-2020"
author: "Chloe Thierstein"
thanks: "Code and data are available at: https://github.com/cthierst/death_registry_analysis.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "The COVID-19 pandemic marked a significant shift in Canadian mortality rates in the year 2020. Using death registry data from three civic centres in the greater Toronto are from 2016 to 2020, we demonstrate that even data from a considerably reliable source may become distorted"
format: pdf
bibliography: references.bib
fig-cap-location: top
---

@@

ggplot(data=cleaned_death_registry_data, aes(x = Year, y = death_licenses, fill = Year)) +
  geom_bar(stat = "identity") +
  theme_classic() + 
  labs(
    x = "Year",
    y = "Death Licenses"
  ) +
  theme(legend.position = "none")+
  scale_fill_brewer(palette="Set3")

@@

ggplot(data=cleaned_death_registry_data, aes(x = Month, y = death_licenses, fill = Year)) +
  theme_classic() +
  geom_bar(stat = "identity") +
  labs(
    x = "Month",
    y = "Death Licenses"
  ) +
  scale_fill_brewer(palette = "Set3")
```

>>>>

---
title: "Death Registrations May Indicate a Discreptency in Reported Data During the COVID-19 Pandemic"
subtitle: "An Analysis of Death Registrations in Toronto from 2016-2020"
author: "Chloe Thierstein"
thanks: "Code and data are available at: https://github.com/cthierst/death_registry_analysis.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "The COVID-19 pandemic marked a significant shift in Canadian mortality rates in the year 2020. Using death registry data from three civic centres in the greater Toronto are from 2016 to 2020, we demonstrate that even data from a considerably reliable source may become distorted"
format: pdf
bibliography: references.bib
fig-cap-location: top
---

@@

ggplot(data=cleaned_death_registry_data, aes(x = Year, y = death_licenses, fill = Year)) +
  geom_bar(stat = "identity") +
  theme_classic() + 
  labs(
    x = "Year",
    y = "Death Licenses"
  ) +
  theme(legend.position = "none")+
  scale_fill_brewer(palette="Set2")

@@

ggplot(data=cleaned_death_registry_data, aes(x = Month, y = death_licenses, fill = Year)) +
  theme_classic() +
  geom_bar(stat = "identity") +
  labs(
    x = "Month",
    y = "Death Licenses"
  ) +
  scale_fill_brewer(palette = "Set2")
```
